---
title: "p8130_hw2"
author: "Renjie Wei"
date: "2020/9/30"
output: html_document
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                   echo=FALSE, warning=FALSE, message=FALSE)
```


```{r}
library(arsenal)
library(dplyr)
library(ggplot2)
options(digits=3)
```
# Problem 1

1) From the data, we can get a table like this:
```{r problem_1, tidy = TRUE}
cancer_mtrx <- matrix(
  c(79,34,113,10,217-10,217,79+10,34+217-10,217+113),
  nr = 3,
  dimnames = list(
    c("Pos","Neg","Total"),
    c("Yes","No","Total")
    
  )
)

cancer_mtrx
```

According to the definition of sensitivity and specificity, we can calculate:
  
  + `sensitivity` = $P(Pos|Yes)$ = 79/113 = `r 79/113 * 100`%.
  + `specificity` = $P(Neg|No)$ = 207/217 = `r 207/217 * 100`%.
  
2) No, the prevalance among the subjects is missing.

3)
  a) 
  
  
  
  
# Problem 2

Let $X $represent the number of the 50 patients who develop prediabetic. Then $X \sim B(50,0.345)$.

1) Probability that none of these patients are prediabetic is:
```{r}
dbinom(0, 50, 0.345)
```

2) Probability that less than 10 patients are prediabetic is:
```{r}
pbinom(9, 50, 0.345)
```

3)
The approximate number of patients number is:
```{r}
round(50*0.345)
```
So, the probability that 34.5% of these patients are prediabetic is:
```{r}
dbinom(17,50,0.345)
```

4)
We can't use an approximation method to caculate the probabilities above, because the conditions of using a Poisson approximation are:
  + $n$ must be larger than 100.
  + Probability of success, $p$, should be smaller than 0.01.

In our situation, $n=50$, $p=0.345$ we can not satisfy any condition. So, in this case, using an approximation is not appropriate.

# Problem 3
```{r}
lambda_us = (5/1000000) * 8300000
lambda_non_his = (6.02/1000000)*8300000*0.428
lambda_blk = (0.31/1000000)*8300000*0.243
lambda_asian = (0.39/1000000)*8300000*0.14
```
a. Let $X$, a random variable denoting the number of uveal melanoma cases in NYC. Then $X \sim Poi(`r lambda_us`)$.

    The probability that in NYC, exactly 30 cases occur in a given year is:
```{r}
dpois(30, lambda_us)
```

b. 
* Let $X_{White}$ denoting the number of uveal melanoma cases of non-Hispanic Whites in NYC.
  + ${X_{White} \sim Poi(`r lambda_non_his`)}$
* Let $X_{Black}$ denoting the number of uveal melanoma cases of Black in NYC.
  + $X_{Black} \sim Poi(`r lambda_blk`)$ 
* Let $X_{Asian}$ denoting the number of uveal melanoma cases of Asians in NYC.
  + $X_{Asian} \sim Poi(`r lambda_asian`)$ 

# Problem 4
Since the average temperature of patients diagnosed with COVID-19 follow a normal distribution with a mean of 99.9 degrees Fahrenheit and a standard deviation of 0.73 degrees Fahrenheit. We can get:

$$ {{\overline{X}} \sim N(99.9,\frac{0.73^{2}}{{40}})}$$
1) The probability that the sample mean is less than 98:
  
  + $P(\overline{X}<98)=`r pnorm(98,mean=99.9,sd=0.73)`$
  
2) The probability that the sample mean is greater than 100.5:

  + $P(\overline{X}>100.5)=`r 1-pnorm(100.5,mean=99.9,sd=0.73)`$
  
3) The 90th quantile of the sampling distribution of the sample mean:

  + $Z_{90}=`r qnorm(0.90,mean=99.9,sd=0.73)`$
  
4) The cutoff values for the middle 50% of the sampling distribution of the sample mean:
  + $Z_{50}=`r qnorm(0.50,mean=99.9,sd=0.73)`$